onsetsync: An R Package for Onset Synchrony Analysis

### 2023-09-09 paper/paper.Rmd
Update paper.Rmd
install options changes

```{r secret_load, eval=TRUE, echo=FALSE}
# LOADS THIS SECRECTLY FROM THE LOCAL FOLDER
library(onsetsync)
ver <- packageVersion('onsetsync')
```

@@

```{r availability,eval=FALSE}
library(devtools)
devtools::install_github("tuomaseerola/onsetsync")
library(onsetsync)
```

>>>>

```{r secret_load, eval=TRUE, echo=FALSE}
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE)
#library(onsetsync)
ver <- packageVersion('onsetsync')
```

@@

```{r availability,eval=FALSE}
library(devtools)
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE")
library(onsetsync)
```
